Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-06-03 ms.tex
changing notation from x to kx for frequency

We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency as seen in Figure \ref{fig:crossHatchA5}.
We model the two dimensional Fourier amplitude $f(x_i',y_i')$ for one angle $\theta_i$ as
\begin{equation}
f(x'_i,y'_i, a_i, b,c) = a \exp{\left(- |x_i'| / b \right)} \left( \frac{1}{(0.5 c)^2 + y'^2} \right),
\end{equation}
where $x'$ and $y'$ are rotated coordinates, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorenzian full width at half maximum.
For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
\begin{equation}
x'(\theta_i) = (x - x_0) \cos{\theta_i} + (y - y_0) \sin{\theta_i}
\end{equation}
and
\begin{equation}
y'(\theta_i) = -(x - x_0) \sin{\theta_i} + (y - y_0) \cos{\theta_i}.
\end{equation}
We include three angles so that the total power spectral density is
\begin{equation}
f(x,y) = \sum_{i=1}^{i=3} f_i(x'_i(\theta_i),y'_i(\theta_i),a_i,b,c).
\end{equation}

>>>>

We 
We model the crosshatch pattern in the Fourier space because it has a smoother pattern as a function of spatial frequency than in spatial coordinates as seen in Figure \ref{fig:crossHatchA5}.
We model the two dimensional Fourier power spectral density $f(k_{x,i}',k_{y,i}')$ for one angle $\theta_i$ as
\begin{equation}
f(k_{x,i}',k_{y,i}', a_i, b,c) = a \exp{\left(- |k_{x,i}'| / b \right)} \left( \frac{1}{(0.5 c)^2 + k_y'^2} \right),
\end{equation}
where $k_x'$ and $k_y'$ are rotated frequency coordinates coordinates, $a$ is the amplitude, $b$ is the parallel exponential constant and $c$ is the Lorenzian full width at half maximum.
For each of the three angles, there is a set of rotated coordinates centered at $(x_0,y_0)$= (1024,1024) following:
\begin{equation}
k_x'(\theta_i) = k_x \cos{\theta_i} + k_y \sin{\theta_i}
\end{equation}
and
\begin{equation}
k_y'(\theta_i) = -k_x  \sin{\theta_i} + k_y \cos{\theta_i}.
\end{equation}
We include three angles so that the total power spectral density is
\begin{equation}
f(k_x,k_y) = \sum_{i=1}^{i=3} f_i(k_{x,i}'(\theta_i),k_{y,i}'(\theta_i),a_i,b,c).
\end{equation}
